### Heated path

Plot leap-frog steps with associated temperatures:

```{r}
library(tidyverse)
path <- read.csv("./sim_output/path1.csv")
path %>%
    ggplot(aes(x = x, y = y, color = temp)) +
    ggtitle("x = (-0.4, -0.9), p = (0.7, -0.9), L = 200, alpha = 1.04, epsilon = 0.3") +
    geom_path() + scale_color_gradient(low = "blue", high = "red")


path <- read.csv("./sim_output/path2.csv")
path %>%
    ggplot(aes(x = x, y = y, color = temp)) +
    ggtitle("x = (0.1, 1), p = (0.5, 0.8), L = 200, alpha = 1.04, epsilon = 0.3") +
    geom_path() + scale_color_gradient(low = "blue", high = "red")

path <- read.csv("./sim_output/path3.csv")
path %>%
    ggplot(aes(x = x, y = y, color = temp)) +
    ggtitle("Diverges because of NAN") +
    geom_path() + scale_color_gradient(low = "blue", high = "red")
```

Turns out when the temperature gets too high, (q) may wander to coordinates with very low density, making the gradient NaN (as f(x) goes to 0)
There are two ways to handle this: 

    1. Take the next sample to be the current one (as the new proposal is unlikely to be accepted anyway)
    2. Change the functions scale to log (tricky but more "correct") - turns out this is not feasible 

### Tempered transitioning HMC
```{r}
cov1 <- diag(c(1, 1))
cov2 <- diag(c(2, 2))
covs <- list(cov1, cov2)

means <- list(c(1, 1), c(10, 10))
weights <- c(0.5, 0.5)

params <- list("means" = means, "covs" = covs,
               "num_steps" = 200,
               "step_size" = 0.3,
               "alpha" = 1.04,
               "mass" = diag(c(1, 1)))

# samples <- get_samples(c(2, 2), params, weights, n_samples = 10000)
samples <- read.csv("./sim_output/far_modes_hmc_1.4.csv")
samples %>%
    ggplot(aes(x = x, y = y, alpha = 0.3)) + geom_point() + ggtitle("alpha = 1.4, L = 20, epsilon = 0.3")

ts.plot(samples$x)

samples <- read.csv("./sim_output/far_modes_hmc_1.04.csv")
samples %>%
    ggplot(aes(x = x, y = y)) + geom_point() + ggtitle("alpha = 1.04, L = 200, epsilon = 0.3")

ts.plot(samples$x)
```

Note that the particle moves much more freely between the two modes in the second settings. (Maximum temperature ~ 7.1)

### Target raised to a temperature

First try with T = 2, 4, 8, 16, 32, other parameters are kept the same.

It is very difficult for the particle to escape its current mode without increasing the mass matrix. 

```{r}
# T <- c(2, 4, 8, 16, 32)
cov1 <- diag(c(1, 1)) / T
cov2 <- diag(c(2, 2)) / T
covs <- list(cov1, cov2)

means <- list(c(1, 1), c(10, 10))
weights <- c(0.5, 0.5)

params <- list("means" = means, "covs" = covs,
               "num_steps" = 200,
               "step_size" = 0.3,
               "alpha" = 1.0,
               "mass" = diag(c(1, 1)))

path <- read.csv("./sim_output/path_temp_16.csv")
path %>% ggplot(aes(x = x, y = y, color = temp)) + geom_path()
```

### HMC within Gibbs framework

Getting a sample from tempered transitioning HMC under normal settings
```{r}
cov1 <- matrix(c(1, 0.95, 0.95, 1), nrow = 2, byrow = TRUE)
cov2 <- matrix(c(1, -0.95, -0.95, 1), nrow = 2, byrow = TRUE)

covs <- list(cov1, cov2)
means <- list(c(1, 1), c(1, 1))

params <- list("means" = means, "covs" = covs,
               "num_steps" = 10,
               "step_size" = 0.05,
               "alpha" = 1,
               "mass" = diag(c(1, 1)))
class(params) <- "HMC_sim_parameters"

# moved sampling from R to C++ for faster performance
df <- read.csv("./sim_output/correlated_target_n_HMC.csv")
df %>%
    ggplot(aes(x = x, y = y)) + geom_point()
```